From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-02 Pi+/paper/finite.tex
Explain how Lehmer codes are normal forms

\todo{diagram with List (Fin n) being divided into equivalence classes, and Lehmer codes being an image of immersion,
  being the normal form (representative) in each class.}

@@

We can show that the function $\immersion$ gives an equivalence betweeen $\Lehmer[n]$ and $\im{\normf}$.

\begin{proposition}
  \leavevmode
  \begin{enumerate}
    \item For any Lehmer code $c$, $\immersion(c)$ is a normal form with resepct to $\cox*$, that is, $\immersion(c)$ is
          in $\im{\normf}$.
    \item Any element of $\im{\normf}$ can be constructed from a unique Lehmer code by $\immersion$, that is, the fibers
          of $\immersion: \Lehmer[n] \to {\im{\normf}}$ are contractible.
  \end{enumerate}
  Therefore, there is an equivalence between $\Lehmer[n]$ and $\im{\normf}$.
\end{proposition}

>>>>

@@

As an example, let us look at the code $c = (4, 3, 2, 1, 0)$. The list $\immersion(c)$ is then going to be $[0, 1, 0, 2,
1, 0, 3, 2, 1, 0, 4, 3, 2, 1, 0]$. It is a concatenation of a sequence of decreasing lists. Where could a reduction
happen? First, it can't happen inside any of the decreasing components: $\longcancel$ requires repeating elements,
$\longswap$ acts when a smaller number precedes a larger one, and $\longbraid$ has a non-monotone sequence on the left.
This leaves the case of a reduction happening on a fragment that borders two subsequences. Again, $\longcancel$ requires
two equal consecutive numbers, which have to be the last one in some decreasing sequence and the first one in the next
one. But the first number in a sequence is always larger than every number in the sequence before it - which also shows
why $\longswap$ cannot happen. The remaining case of $\longbraid$ is proven on similar grounds, since it requires the
number appearing after the decreasing sequence to be equal to the first one in the sequence.

Using this idea, we can show that the function $\immersion$ gives an equivalence betweeen $\Lehmer[n]$ and
$\im{\normf}$.

\begin{proposition}
  \leavevmode
  \begin{enumerate}
    \item For any Lehmer code $c$, $\immersion(c)$ is a normal form with resepct to $\longcox*$, that is, $\immersion(c)$ is
          in $\im{\normf}$.
    \item Any element of $\im{\normf}$ can be constructed from a unique Lehmer code by $\immersion$, that is, the fibers
          of $\immersion: \Lehmer[n] \to {\im{\normf}}$ are contractible.
  \end{enumerate}
  Therefore, there is an equivalence between $\Lehmer[n]$ and $\im{\normf}$.
\end{proposition}
